Understanding LIME

### 2019-09-06 README.Rmd
finished documenting the LIME R package in journal 02

- Graphics Group
    - email list

@@

- go back through LIME procedure and update with new understanding (such as d' can be larger than d)
- add an assert_that statement in the code to check if the LIME package is changing
- point out differences and similarities from the other paper (such as normal sampling)
- code up Laugel et al's work
- read through papers giving an overview of the current explanation methods
- check to see if there a paper showing how ridge regression is affected by sample size changes
- try fitting the ridge regression with the observed data only to see how it compares to the model fit with the ridge regression

>>>>

- Graphics Group
    - email list
    - what should we do about gganimate/Halloween?

@@

- code up Laugel et al's work
- read through papers giving an overview of the current explanation methods
- check to see if there a paper showing how ridge regression is affected by sample size changes
- try fitting the ridge regression with the observed data only to see how it compares to the model fit with the ridge regression

### 2019-09-06 journals/02-understanding_lime/02-understanding_lime.Rmd
finished documenting the LIME R package in journal 02

# Original Paper {.tabset}

@@

### Notation

@@

### Goal of LIME

@@

### Procedure

@@

### Comment on Faithfulness

@@

### Data and Model

### Linear Regression Explainer

### Ridge Regression Explainer

@@

1. If `preprocess` is NULL, then set it to the identity function. Either way, check to make sure that it is a function.
2. Create an explainer object.
3. Determine the type of each of the features (e.g. integer, numeric, etc.). If any of the variables are constants, a warning is returned. If the feature type is unknown, an error is returned.
4. Create bins for numeric and inter type variables. If `quantile_bins = TRUE`, then `n_bins` bins are created using quantiles. Otherwise, `n_bins` equally spaced bins are created. If `quantile_bins = TRUE` and `n_bins` < 3, then a warning is produced ("does not contain enough variance to use quantile binning. Using standard binning instead.") and `n_bins` equally spaced bins are returned.
5. Determine the "distribution" for each feature. The method used is based on the type of variable. 
    - Integer: nothing
    - Numeric: If `bin_continuous`, then determine the
    proportion of observations in each bin. If
    `use_density=TRUE`, then kernel a kernel density
    approximation is used to estimate the distribution.
    Otherwise, the mean and standard deviation of each 
    of the features is computed.
    - Character: nothing
    - Logical: nothing
    - Factor: Determine the proportion in each category.
6. Assign some attributes to the explainer object, and return the explainer object.

@@

```{r}
# Print the lime function (and check to see if there have been any changes)
func_check("lime.data.frame", "0.5.0")
```

@@

---------

- Predictions for the testing data using the random forest model are computed.
     + The random forest model `rtrees` is used to make a prediction for the observation from the test dataset and each of the $n=5000$ samples as to whether or not the comparison of the two bullets in the test case are a match. Since the random forest is a classification model, `lime` is set to return the prediction probabilities.

- Similarity score between the observation in the testing data and each of the $n=5000$ sampled values are obtained.
    + The way that the similarity score is computed depends on the type of feature. Since all of the features in the Hamby 224 test dataset are continuous, the simulated values are first converted into 0-1 features where a 1 indicates that the feature from the simulated value falls in the same bin as the observed data point and a 0 indicates that the feature is not in the same bin as the observed data point. Then, by default, the Gower distance is used to compute the similarity score. (using the `gower` package in R)

- Feature selection is performed by fitting some type of regression model weighted by the similarity scores is to the simulated data and the observed value. The 0-1 versions of the features are used.
    + The user can specify the number of features, $m$, they would like to select to explain the prediction. `lime` supports the following options for feature selection
      * forward selection with ridge regression
      * highest weight with ridge regression
      * LASSO model
      * tree model
      * default: forward selection if $m\le6$ with a ridge regression model, highest weight with ridge regression otherwise

- A ridge regression model is fit as the simple model by regressing the prediction probabilities on the $m$ selected predictor variables and weighted by the similarity scores. If the response is categorical, the user can select how many categories and which categories they want to explain.
  $$P(Match = TRUE) = \beta_0 + 
  \beta_1 \cdot I\left[X_1 \in \mbox{obs bin}\right] + 
  \beta_2 \cdot I\left[X_2 \in \mbox{obs bin}\right] + 
  \beta_3 \cdot I\left[X_3 \in \mbox{obs bin}\right]$$
For the prediction of interest, 
  $$P(Match = TRUE) = \beta_0 + \beta_1 + \beta_2 + \beta_3.$$
- The feature weights are extracted and used as the explanations.

Note: I realized that if `bin_continuous = FALSE`, then bins are not used at all. Instead, a kernel density estimator is used to sample from the distribution (or a normal distribution if specified), and then the ridge regression models are fit without "numerified" values.

@@

```{r}
# Print the explain function (and check to see if there have been any changes)
func_check("explain.data.frame", "0.5.0")
```

@@

@@

#### Info

The *lime* package provides a variety of functions for extracting the model type from the complex model to be explained. The function `model_type` is an overarching function that leads to the specific functions for determining the model type. The specific functions vary based on what package was used to fit the model.

Here is information from the package documentation about models supported by *lime*.

@@

@@

```{r}
getAnywhere(model_type)
```

#### Model Specific Functions

```{r}
getAnywhere(model_type)
getAnywhere(model_type.default)
getAnywhere(model_type.lime_classifier)
getAnywhere(model_type.lime_regressor)
getAnywhere(model_type.train)
getAnywhere(model_type.model_fit)
getAnywhere(model_type.WrappedModel)
getAnywhere(model_type.xgb.Booster)
getAnywhere(model_type.lda)
getAnywhere(model_type.keras.engine.training.Model)
getAnywhere(model_type.H2OModel)
getAnywhere(model_type.ranger)
```

@@

```{r}
# Print the explain function (and check to see if there have been any changes)
func_check("output_type", "0.5.0")
```

@@

```{r exp_kernel}
# Print the exp_kernel function (and check to see if there have been any changes)
if(!file.exists("../../../data/lime_functions/exp_kernel_v0.5.0.rds")) {
  saveRDS(object = getAnywhere(exp_kernel),
          file = "../../../data/lime_functions/exp_kernel_v0.5.0.rds")
  getAnywhere(exp_kernel)
} else {
  exp_kernel_v0.5.0 <- readRDS("../../../data/lime_functions/exp_kernel_v0.5.0.rds")  
  if(assert_that(are_equal(exp_kernel_v0.5.0, getAnywhere(exp_kernel)))){
    getAnywhere(exp_kernel)
  } 
}
```

@@

@@

2. Create the perturbations based on the type of variable and using the feature distribution determined by the lime function. The cases are as follows.
    - numeric variable and the feature distribution contains all NAs: the observed cases get repeated `n_permutations` times
    - numeric variable and `bin_continuous = TRUE`: 
    sample from 1:number of bin cuts with replacement for
    nrows times using the probability from the variable 
    distribution sample from a uniform(0,1) distribution
    and then multiply by the difference in bin cuts of
    the appropriate bin and add the quantile associated
    with the bin
    - numeric variable, `bin_continuous = FALSE`, and `use_density = TRUE`: 
    - numeric variable, `bin_continuous = FALSE`, and `use_density = FALSE`: randomly sample from a normal distribution, multiply by the sd of the feature distribution, and add the mean 
    - character variable: sample from the names of the levels in the variable based on the probability of the variable distribution
    - logical variable: 
    - factor variable: sample from the names of the levels in the variable based on the probability of the variable distribution and convert the samples to factors 
    - date: 
    - integer variable: round the permutations to the nearest integer
3. Give the permutations the same name as the variables
4. Add the cases back into the data frame of the permutations
5. Return the permutations.

@@

```{r}
if(!file.exists("../../../data/lime_functions/permute_cases_v0.5.0.rds")) {
  saveRDS(object = getAnywhere(permute_cases.data.frame),
          file = "../../../data/lime_functions/permute_cases_v0.5.0.rds")
  getAnywhere(permute_cases.data.frame)
} else {
  permute_cases_v0.5.0 <- readRDS("../../../data/lime_functions/permute_cases_v0.5.0.rds")  
  if(assert_that(are_equal(permute_cases_v0.5.0, getAnywhere(permute_cases.data.frame)))){
    getAnywhere(permute_cases.data.frame)
  } 
}
```

@@

@@

### The Data

@@

### Subsampled Bins

@@

### Tree Based Bins

>>>>

# Original Paper

@@

## Notation

@@

## Goal of LIME

@@

## Procedure

@@

## Comment on Faithfulness

@@

@@

1. If `preprocess` is NULL, then set it to the identity function. Either way, check to make sure that it is a function.

        if (is.null(preprocess)) 
          preprocess <- function(x) x
        assert_that(is.function(preprocess))

2. Create an explainer object.

        explainer <- c(as.list(environment()), list(...))
        explainer$x <- NULL

3. Determine the type of each of the features (e.g. integer, numeric, etc.). If any of the variables are constants, a warning is returned. If the feature type is unknown, an error is returned.

        explainer$feature_type <- setNames(sapply(x, function(f) {
          if (is.integer(f)) {
            if (length(unique(f)) == 1) 
                 "constant"
             else "integer"
          }
          else if (is.numeric(f)) {
            if (length(unique(f)) == 1) 
                 "constant"
            else "numeric"
          }
          else if (is.character(f)) {
            "character"
          }
          else if (is.factor(f)) {
            "factor"
          }
          else if (is.logical(f)) {
            "logical"
          }
          else if (inherits(f, "Date") || inherits(f, "POSIXt")) {
            "date_time"
          }
          else {
            stop("Unknown feature type", call. = FALSE)
          }
        }), names(x))
        if (any(explainer$feature_type == "constant")) {
          warning("Data contains numeric columns with zero variance", 
            call. = FALSE)
        }

4. Create bins for numeric and inter type variables. If `quantile_bins = TRUE`, then `n_bins` bins are created using quantiles. Otherwise, `n_bins` equally spaced bins are created. If `quantile_bins = TRUE` and `n_bins` < 3, then a warning is produced ("does not contain enough variance to use quantile binning. Using standard binning instead.") and `n_bins` equally spaced bins are returned.

        explainer$bin_cuts <- setNames(lapply(seq_along(x), function(i) {
          if (explainer$feature_type[i] %in% c("numeric", "integer")) {
            if (quantile_bins) {
              bins <- quantile(x[[i]], seq(0, 1, length.out = n_bins + 
                1), na.rm = TRUE)
              bins <- bins[!duplicated(bins)]
              if (length(bins) < 3) {
                warning(names(x)[i], " does not contain enough variance to use
                quantile binning. Using standard binning instead.", 
                  call. = FALSE)
                d_range <- range(x[[i]], na.rm = TRUE)
                bins <- seq(d_range[1], d_range[2], length.out = n_bins + 1)
              }
              bins
            }
            else {
              d_range <- range(x[[i]], na.rm = TRUE)
              seq(d_range[1], d_range[2], length.out = n_bins + 1)
            }
          }
        }), names(x))

5. Determine the "distribution" for each feature. The method used is based on the type of variable. 
    - Integer: nothing
    - Numeric: If `bin_continuous`, then determine the
    proportion of observations in each bin. If
    `use_density=TRUE`, then kernel a kernel density
    approximation is used to estimate the distribution.
    Otherwise, the mean and standard deviation of each 
    of the features is computed.
    - Character: nothing
    - Logical: nothing
    - Factor: Determine the proportion in each category.

          explainer$feature_distribution <- setNames(lapply(seq_along(x),
              function(i) {
                switch(explainer$feature_type[i], 
                  integer = , 
                  numeric = if (bin_continuous) {
                    table(cut(x[[i]], unique(explainer$bin_cuts[[i]]), 
                      labels = FALSE, include.lowest = TRUE))/nrow(x)
                  } else if (use_density) {
                    density(x[[i]])
                  } else {
                   c(mean = mean(x[[i]], na.rm = TRUE), sd = sd(x[[i]], 
                     na.rm = TRUE))
                  }, character = , logical = , factor = table(x[[i]])/nrow(x), 
                   NA)
            }), names(x))

6. Assign some attributes to the explainer object, and return the explainer object.

        structure(explainer, class = c("data_frame_explainer", "explainer", 
          "list"))

@@

```{r}
# Print the function (and check to see if there have been any changes)
func_check("lime.data.frame", "0.5.0")
```

@@

8. Obtains predictions for all of the permutated data points based on the original model using the [`predict_model`](#predict_model) function.

        case_res <- predict_model(explainer$model, 
          explainer$preprocess(case_perm),
          type = o_type, ...)
        case_res <- set_labels(case_res, explainer$model)

9. Creates indicies for each of the perturbations and dividing them into groups based on which new prediction case they correspond to

        case_ind <- split(seq_len(nrow(case_perm)), rep(seq_len(nrow(x)), each = n_permutations))

10. Fill in the results obejct

        res <- lapply(seq_along(case_ind), function(ind) {

11. Create a vector of indicies for one of the observations

        i <- case_ind[[ind]]

12. If the distance function is specified to be "gower", then compute the distance between the case of interest and each observation in the permuted dataset. These distances get raised to whatever the specified `gower_pow` is. Then these values are subtracted from one so that observations closer to the case of interest have a higher "weight" associated with them.

        if (dist_fun == "gower") {
          sim <- 1 - (gower_dist(case_perm[i[1], , drop = FALSE], 
            case_perm[i, , drop = FALSE]))^gower_pow
        }

13. Turns the factor and character variables into numeric variables and determines whether a permutation falls into the test data bin if bins_continuous is set to TRUE. This uses the [`numerify`](#numerify) function.

        perms <- numerify(case_perm[i, ], explainer$feature_type, explainer$bin_continuous, explainer$bin_cuts)

14. If the distance is not set to "gower", then distance between the case of interest and the permutations is computed using the kernel function. This also makes use of the [`feature_scale`](#feature_scale) function.

        if (dist_fun != "gower") {
          sim <- kernel(c(0, dist(feature_scale(perms, explainer$feature_distribution, 
            explainer$feature_type, explainer$bin_continuous), 
            method = dist_fun)[seq_len(n_permutations - 1)]))
        }

15. Perform feature selection and fit a model to the permutations using these important variables using the function [`model_permutations`](#model_permutations).

        res <- model_permutations(as.matrix(perms), case_res[i, , drop = FALSE], sim, labels, n_labels, n_features, feature_select)

16. Finish filling in the rest of the results object with information about bins and such. This makes use of the [`describe_feature`](#describe_feature) function.

        res$feature_value <- unlist(case_perm[i[1], res$feature])
        res$feature_desc <- describe_feature(res$feature, case_perm[i[1], ], explainer$feature_type, 
          explainer$bin_continuous, explainer$bin_cuts)
        guess <- which.max(abs(case_res[i[1], ]))
        res$case <- rownames(x)[ind]
        res$label_prob <- unname(as.matrix(case_res[i[1], ]))[match(res$label, colnames(case_res))]
        res$data <- list(as.list(case_perm[i[1], ]))
        res$prediction <- list(as.list(case_res[i[1], ]))
        res$model_type <- m_type
        res

17. Join the results and assign names to the columns

        res <- do.call(rbind, res)
        res <- res[, c('model_type', 'case', 'label', 'label_prob', 'model_r2', 
                       'model_intercept', 'model_prediction', 'feature', 'feature_value', 
                       'feature_weight', 'feature_desc', 'data', 'prediction')]
        if (m_type == 'regression') {
          res$label <- NULL
          res$label_prob <- NULL
          res$prediction <- unlist(res$prediction)
        }

18. Return the results object

        res

@@

```{r}
# Print the function (and check to see if there have been any changes)
func_check("explain.data.frame", "0.5.0")
```

@@

These are listed in the order that they are used.

@@

1. The function `model_type` is an overarching function that leads to the specific functions for determining the model type.

        model_type <- function (x, ...) {
                    UseMethod("model_type")
                  }

    The specific functions vary based on what package was used to fit the model. Here is information from the package documentation about models supported by *lime*.

@@

2. Apply the model specific function to determine the model type.

    - **default**

          stop("The class of model must have a model_type method. See ?model_type to get an overview of models supported out of the box", call. = FALSE)

    - **lime classifier**

            "classification"

    - **lime regressor**

            "regression"

    - **train**

            tolower(x$modelType)

    - **model fit**

            x$spec$mode

    - **Wrapped Model**

            switch(x$learner$type, classif = "classification", regr = "regression", 
              surv = "survival", cluster = "clustering", multilabel = "multilabel")

    - **xgb Booster**

            obj <- x$params$objective
            if (is.null(obj)) 
              return("regression")
            if (is.function(obj)) 
              stop("Unsupported model type", call. = FALSE)
            type <- strsplit(obj, ":")[[1]][1]
            switch(type, reg = "regression", binary = "classification", 
              multi = "classification", stop("Unsupported model type", 
              call. = FALSE))

    - **lda**

            "classification"

    - **keras**

            if (!requireNamespace("keras", quietly = TRUE)) {
              stop("The keras package is required for predicting keras models")
            }
            num_layers <- length(x$layers)
            if (keras::get_config(keras::get_layer(x, index = num_layers))$activation == "linear") {
              "regression"
            }
            else {
              "classification"
            }

    - **ranger**

            ranger_model_class <- x$treetype
            if (ranger_model_class == "Probability estimation" || ranger_model_class == "Classification") {
              return("classification")
            }
            else if (ranger_model_class == "Regression") {
              return("regression")
            }
            else {
              stop(paste0("ranger model class \"", ranger_model_class, 
                "\" is not currently supported."))
            }

@@

```{r}
func_check("model_type", "0.5.0")
func_check("model_type", "0.5.0")
func_check("model_type.default", "0.5.0")
func_check("model_type.lime_classifier", "0.5.0")
func_check("model_type.lime_regressor", "0.5.0")
func_check("model_type.train", "0.5.0")
func_check("model_type.model_fit", "0.5.0")
func_check("model_type.WrappedModel", "0.5.0")
func_check("model_type.xgb.Booster", "0.5.0")
func_check("model_type.lda", "0.5.0")
func_check("model_type.keras.engine.training.Model", "0.5.0")
func_check("model_type.H2OModel", "0.5.0")
func_check("model_type.ranger", "0.5.0")
```

@@

```{r}
# Print the function (and check to see if there have been any changes)
func_check("output_type", "0.5.0")
```

@@

```{r}
# Print the function (and check to see if there have been any changes)
func_check("exp_kernel", "0.5.0")
```

@@

- `cases`: the object `x` from `explain.data.frame` (new obs to explain)
- `n_permutations`: the object `n_permutations` from `explain.data.frame` (number of perturbations)
- `feature_distribution`: the object `explainer$feature_distribution` (the distribution of each feature computed from `lime.data.frame`)
- `bin_continuous`: the object `explainer$bin_continuous` determined from `lime.data.frame`
- `bin_cuts`: the object `explainer$bin_cuts` determined from `lime.data.frame`
- `use_density`: the object `explainer$use_density` determined from `lime.data.frame`

@@

2. Create the perturbations based on the type of variable and using the feature distribution determined by the lime function. The cases are as follows.

        perm <- as.data.frame(lapply(seq_along(cases), function(i) {

    - **numeric variable and feature distribution contains all NAs**: the observed cases get repeated `n_permutations` times

            perms <- if (is.numeric(cases[[i]]) && identical(is.na(feature_distribution[[i]]), TRUE)) {
            rep(cases[[i]], each = n_permutations)
            }

    - **numeric variable and `bin_continuous = TRUE`**: 
    sample from 1:number of bin cuts with replacement for
    nrows times using the probability from the variable 
    distribution sample from a uniform(0,1) distribution
    and then multiply by the difference in bin cuts of
    the appropriate bin and add the quantile associated
    with the bin

            else if (is.numeric(cases[[i]]) && bin_continuous) {
              bin <- sample(seq_along(feature_distribution[[i]]), 
                nrows, TRUE, as.numeric(feature_distribution[[i]]))
              diff(bin_cuts[[i]])[bin] * runif(nrows) + bin_cuts[[i]][bin]
            }

    - **numeric variable, `bin_continuous = FALSE`, and `use_density = TRUE`**:

            else if (is.numeric(cases[[i]]) && use_density) {
              width <- diff(feature_distribution[[i]]$x[c(1, 2)])/2
              sample(feature_distribution[[i]]$x, nrows, TRUE, 
                feature_distribution[[i]]$y) + runif(nrows, -width, width)
            }

    - **numeric variable, `bin_continuous = FALSE`, and `use_density = FALSE`**: randomly sample from a normal distribution, multiply by the sd of the feature distribution, and add the mean

            else if (is.numeric(cases[[i]])) {
               rnorm(nrows) * feature_distribution[[i]]["sd"] + 
                   feature_distribution[[i]]["mean"]
            }

    - **character variable**: sample from the names of the levels in the variable based on the probability of the variable distribution

            else if (is.character(cases[[i]])) {
               sample(names(feature_distribution[[i]]), nrows, TRUE, 
                   as.numeric(feature_distribution[[i]]))
            }

    - **logical variable**:

            else if (is.logical(cases[[i]])) {
               sample(as.logical(names(feature_distribution[[i]])), 
                   nrows, TRUE, as.numeric(feature_distribution[[i]]))
            }

    - **factor variable**: sample from the names of the levels in the variable based on the probability of the variable distribution and convert the samples to factors

            else if (is.factor(cases[[i]])) {
              x <- sample(names(feature_distribution[[i]]), nrows, 
                TRUE, as.numeric(feature_distribution[[i]]))
              factor(x, levels = names(feature_distribution[[i]]))
            }

    - **date**:

            else if (inherits(cases[[i]], "Date") || inherits(cases[[i]], "POSIXt")) {
              rep(cases[[i]], each = n_permutations)
            }

    - **integer variable**: round the permutations to the nearest integer

            if (is.integer(cases[[i]])) {
              as.integer(round(perms))
            }

    - **other**:

            } else {
              perms
            }
            }), stringsAsFactors = FALSE)

3. Give the permutations the same name as the variables

        names(perm) <- names(cases)

4. Add the cases back into the data frame of the permutations

        perm[seq.int(1, by = n_permutations, length.out = nrow(cases)), ] <- cases

5. Return the permutations.

        perm

@@

```{r}
# Print the function (and check to see if there have been any changes)
func_check("permute_cases.data.frame", "0.5.0")
```

### `predict_model` {#predict_model .tabset}

- `x`: a model
- `newdata`: the new observations to predict
- `type`: either `'raw'` to indicate predicted values, or `'prob'` to indicate class probabilities

1. Determine which `predict_model` function to use based on the model type

        predict_model <- function(x, newdata, type, ...) {
          UseMethod('predict_model')
        }

2. Make predictions appropriately based on the model type

    - **Default**

            predict_model.default <- function(x, newdata, type, ...) {
              p <- predict(x, newdata = newdata, type = type, ...)
              if (type == 'raw') 
                p <- data.frame(Response = p, stringsAsFactors = FALSE)
              as.data.frame(p)
            }

    - **Model Fit** (?)

            predict_model.model_fit <- function (x, newdata, type, ...) {
              if (type == "raw") 
                type <- "numeric"
                p <- predict(x, new_data = newdata, type = type, ...)
              if (type == "raw") {
                p <- data.frame(Response = p[[1]], stringsAsFactors = FALSE)
              }
              else if (type == "prob") {
                names(p) <- sub(".pred_", "", names(p))
              }
              p
            }

    - **Wrapped Model**

            predict_model.WrappedModel <- function (x, newdata, type, ...) {
              if (!requireNamespace("mlr", quietly = TRUE)) {
                stop("mlr must be available when working with WrappedModel models")
              }
              p <- predict(x, newdata = newdata, ...)
              switch(type, raw = data.frame(Response = mlr::getPredictionResponse(p), 
                stringsAsFactors = FALSE), prob = mlr::getPredictionProbabilities(p, 
                p$task.desc$class.levels), stop("Type must be either \"raw\" or \"prob\"", 
              call. = FALSE))
            }

    - **xbg Booster**

            predict_model.xgb.Booster <- function (x, newdata, type, ...) {
              if (!requireNamespace("xgboost", quietly = TRUE)) {
                stop("The xgboost package is required for predicting xgboost models")
              }
              if (is.data.frame(newdata)) {
                newdata <- xgboost::xgb.DMatrix(as.matrix(newdata))
              }
              p <- data.frame(predict(x, newdata = newdata, reshape = TRUE, ...), 
                stringsAsFactors = FALSE)
              if (type == "raw") {
                names(p) <- "Response"
              }
              else if (type == "prob") {
                if (ncol(p) == 1) {
                  names(p) = "1"
                  p[["0"]] <- 1 - p[["1"]]
                }
                else {
                  names(p) <- as.character(seq_along(p))
                }
              }
              p
            }

    - **lda**

            predict_model.lda <- function(x, newdata, type, ...) {
              res <- predict(x, newdata = newdata, ...)
              switch(
              type,
              raw = data.frame(Response = res$class, stringsAsFactors = FALSE),
              prob = as.data.frame(res$posterior, check.names = FALSE)
              )
            }

    - **keras**

            predict_model.keras.engine.training.Model <- function (x, newdata, type, ...) {
              if (!requireNamespace("keras", quietly = TRUE)) {
                stop("The keras package is required for predicting keras models")
              }
              res <- predict(x, as.array(newdata))
              if (type == "raw") {
                data.frame(Response = res[, 1])
              }
              else {
                if (ncol(res) == 1) {
                res <- cbind(1 - res, res)
              }
              colnames(res) <- as.character(seq_len(ncol(res)))
              as.data.frame(res, check.names = FALSE)
              }
            }

    - **H2O Model**

            predict_model.H2OModel <- ## function (x, newdata, type, ...) {
               if (!requireNamespace("h2o", quietly = TRUE)) {
                   stop("The h2o package is required for predicting h2o models")
               }
               pred <- h2o::h2o.predict(x, h2o::as.h2o(newdata))
               h2o_model_class <- class(x)[[1]]
               if (h2o_model_class %in% c("H2OBinomialModel", "H2OMultinomialModel")) {
                   return(as.data.frame(pred[, -1]))
               }
               else if (h2o_model_class == "H2ORegressionModel") {
                   ret <- as.data.frame(pred[, 1])
                   names(ret) <- "Response"
                   return(ret)
               }
               else {
                   stop("This h2o model is not currently supported.")
               }
           }

```{r}
# Print the function (and check to see if there have been any changes)
func_check("predict_model", "0.5.0")
func_check("predict_model.default", "0.5.0")
func_check("predict_model.model_fit", "0.5.0")
func_check("predict_model.WrappedModel", "0.5.0")
func_check("predict_model.xgb.Booster", "0.5.0")
func_check("predict_model.lda", "0.5.0")
func_check("predict_model.keras.engine.training.Model", "0.5.0")
func_check("predict_model.H2OModel", "0.5.0")
func_check("predict_model.ranger", "0.5.0")
```

### `numerify` {#numerify .tabset}

- `x`: object `case_perm` with the perturbed values 
- `type`: the `explainer$feature_type` object 
- `bin_continuous`: the value of `explainer$bin_continuous` 
- `bin_cuts`: the value of `explainer$bin_cuts`

1. Apply the function below to each observation in the perturbed dataset.

        setNames(as.data.frame(lapply(seq_along(x), function(i) {

2. If the variable is a character, factor, or logical change it to a numeric variable.

        if (type[i] %in% c("character", "factor", "logical")) {
          as.numeric(x[[i]] == x[[i]][1])
        }

3. If the variable is some other type and `bin_continuous=TRUE`, then put the bin cuts into a variable called cuts, set the first and last bin cuts to -inf and inf, respectively, determine which bin each permutation falls into, and determine whether a permution falls into the test data observation bin of interest.

        else {
          if (bin_continuous) {
            cuts <- bin_cuts[[i]]
            cuts[1] <- -Inf
            cuts[length(cuts)] <- Inf
            xi <- cut(x[[i]], unique(cuts), include.lowest = T)
            as.numeric(xi == xi[1])

4. If the variable is some other type and `bin_continuous=FALSE`, then just return the permutations.

          } else {
            x[[i]]
          }
        }
        }), stringsAsFactors = FALSE), names(x))

```{r}
# Print the function (and check to see if there have been any changes)
func_check("numerify", "0.5.0")
```

### `feature_scale` {#feature_scale .tabset}

- `x` = `perms`
- `distribution` = `explainer$feature_distribution`
- `type` = `explainer$feature_type`
- `bin_continuous` = `explainer$bin_continuous`

Scales the distribuiton of the numeric permutions if bin_continuous was set to FALSE.

```{r}
# Print the function (and check to see if there have been any changes)
func_check("feature_scale", "0.5.0")
```

### `model_permutations` {#model_permutations .tabset}

- `x`: the `as.matrix(perms)` object with the perturbations
- `y`: `case_res[i, , drop = FALSE]`
- `weights`: the weights `sim`
- `labels`: the `labels` object
- `n_labels`: the `n_labels` object
- `n_features`: the `n_features` object
- `feature_method`: the `feature_select` object

1. If all of the weights are 0 (no difference from the case of interest), then return an error.

        if (all(weights[-1] == 0)) {
          stop("All permutations have no similarity to the original observation. 
          Try setting bin_continuous to TRUE and/or increase kernel_size", 
          call. = FALSE)
        }

2. Create labels if `n_labels` is not NULL.

        if (!is.null(n_labels)) {
          labels <- names(y)[order(as.data.frame(y)[1, ], decreasing = TRUE)[seq_len(n_labels)]]
        }

3. Something about missing values (?)

        x <- x[, colSums(is.na(x)) == 0 & apply(x, 2, var) != 0, drop = FALSE]

4. If the response has the same value for all permutations, then an error is returned.

        res <- lapply(labels, function(label) {
          if (length(unique(y[[label]])) == 1) {
            stop("Response is constant across permutations. Please check your model", 
            call. = FALSE)
        }

5. Select which variables are important for the model using the [`select_features`](#select_features) function.

        features <- select_features(feature_method, x, y[[label]], weights, n_features)

6. `glmnet` does not allow `n_features=1`, so in this case the model must be fit separately. This is done by 
creating a matrix with a column of 1s for the intercept and the selected variables for the other columns, fiting a model with the probability as the response and the selected variables as the predictors, computing the r2 values, and extracting the intercept, non-intercept coefficients, and model prediction for the case of interest.

        if (length(features) == 1) {
          x_fit = cbind("(Intercept)" = rep(1, nrow(x)), x[, features, drop = FALSE])
          fit <- glm.fit(x = x_fit, y = y[[label]],  weights = weights, family = gaussian())
          r2 <- 1 - fit$deviance/fit$null.deviance
          coefs <- coef(fit)
          intercept <- coefs[1]
          coefs <- coefs[-1]
          model_pred <- fit$fitted.values[1]

7. When `n_features` > 1, fit the ridge regression model using `glmnet` when the order of the observations shuffled, and extract the same items as in Step 6.

        } else {
          shuffle_order <- sample(length(y[[label]])) # glm is sensitive to the order of the examples
          fit <- glmnet(x[shuffle_order, features], y[[label]][shuffle_order], weights = weights[shuffle_order], 
            alpha = 0, lambda = 0.001)
          r2 <- fit$dev.ratio
          coefs <- coef(fit)
          intercept <- coefs[1, 1]
          coefs <- coefs[-1, 1]
          model_pred <- predict(fit, x[1, features, drop = FALSE])[1]
        }

8. Finally, put the values from above into a data frame.

        data.frame(
          label = label,
          feature = names(coefs),
          feature_weight = unname(coefs),
          model_r2 = r2,
          model_intercept = intercept,
          model_prediction = model_pred,
          stringsAsFactors = FALSE
        )
        })

10. Bind all of the results associated with different cases.

        do.call(rbind, res)

```{r}
# Print the function (and check to see if there have been any changes)
func_check("model_permutations", "0.5.0")
```

### `select_features` {#select_features .tabset}

- `method`: `feature_method`
- `x`: `x`
- `y`: `y[[label]]`
- `weights`: `weights`
- `n_features`: `n_features`

Performs features selection using the specified method. Note that this is based on a handful of other [functions](#select) including the `feature_selection_method`.

        if (n_features >= ncol(x)) {
          return(seq_len(ncol(x)))
        }
        method <- match.arg(method, feature_selection_method())
        switch(
          method,
          auto = if (n_features <= 6) {
            select_features("forward_selection", x, y, weights, n_features)
          } else {
            select_features("highest_weights", x, y, weights, n_features)
          },
          none = seq_len(nrow(x)),
          forward_selection = select_f_fs(x, y, weights, n_features),
          highest_weights = select_f_hw(x, y, weights, n_features),
          lasso_path = select_f_lp(x, y, weights, n_features),
          tree = select_tree(x, y, weights, n_features),
          stop("Method not implemented", call. = FALSE)
        )

```{r}
# Print the function (and check to see if there have been any changes)
func_check("select_features", "0.5.0")
func_check("feature_selection_method", "0.5.0")
```

### `select_` {#select .tabset}

#### Options

- Forward selection: `select_f_fs`
- Heighest weights: `select_f_hw`
- Lasso path: `select_f_lp`
- Tree: `select_tree`

#### `select_f_fs`

```{r}
# Print the function (and check to see if there have been any changes)
func_check("select_f_fs", "0.5.0")
```

#### `select_f_hw`

```{r}
# Print the function (and check to see if there have been any changes)
func_check("select_f_hw", "0.5.0")
```

#### `select_f_lp`

```{r}
# Print the function (and check to see if there have been any changes)
func_check("select_f_lp", "0.5.0")
```

#### `select_tree`

```{r}
# Print the function (and check to see if there have been any changes)
func_check("select_tree", "0.5.0")
```

### `describe_feature` {#describe_feature .tabset}

- `feature` = `res$feature`
- `case` = `case_perm[i[1], ]`
- `type` = `explainer$feature_type`
- `bin_continuous` = `explainer$bin_continuous`
- `bin_cuts` = `explainer$bin_cuts`

```{r}
# Print the function (and check to see if there have been any changes)
func_check("describe_feature", "0.5.0")
```

@@

## Data and Model

## Linear Regression Explainer

## Ridge Regression Explainer

@@

## The Data

@@

## Subsampled Bins

@@

## Tree Based Bins
